---
title: "1_PrepareData"
output: html_document
date: "2024-05-06"
---
```{r setup, include=FALSE}

rm(list = ls())
knitr::opts_chunk$set(error = FALSE,echo=FALSE, message=FALSE, warning=FALSE,fig.height = 9)

rm(list = ls())
project_dir = rstudioapi::getActiveProject();
src_dir = file.path(project_dir, "src/R", fsep="/")
llr_dir = file.path(project_dir, "src/LLR", fsep="/")

data_dir = file.path(project_dir, "data","Exp2_pilots","3_M2_V2", fsep="/")
result_dir = file.path(project_dir, "results","Exp2_pilots","3_M2_V2", fsep="/")


source(file.path(src_dir,"envSetup.R",fsep="/"), local = knitr::knit_global())
source(file.path(src_dir,"funcDef.R",fsep="/"), local = knitr::knit_global())
source(file.path(src_dir,"setPlotDefault.R",fsep="/"), local = knitr::knit_global())
```

# Attention Check
Plot attention check results and see if any need to be excluded from analyses
```{r,fig.height=3,fig.width=8}
pilot_data = read.csv(file.path(data_dir,"task_data.csv",fsep="/"))
attention_check_data = pilot_data%>%
  filter(ctrl_ept==0)
attention_check_sum = attention_check_data%>%
  aggregate_data(groupbyvars=c("subid","expt_session"),
                 yvars="resp_correct",
                 stats = c("sum","n","mu"))%>%
  change_cols_name(oldnames=c("sum_resp_correct","n_resp_correct","mu_resp_correct"),
                   newnames=c("n_correct","n_totaltrials","accuracy"))
attention_check_sum = attention_check_sum%>%
  mutate(session_str = factor(expt_session,
                              levels=c(0,1),
                              labels=c(sprintf("session1 (%d trials)",unique(filter(attention_check_sum,expt_session==0)$n_totaltrials)),
                                       sprintf("session2 (%d trials)",unique(filter(attention_check_sum,expt_session==1)$n_totaltrials))
                                       )
                              ))
  

remove_sub = unique(filter(attention_check_sum,accuracy<0.5)$subid) #==min(attention_check_sum$accuracy)
attention_check_sum = attention_check_sum%>%
  mutate(x.label = paste("<span style = 'color: ",
                         ifelse(subid%in%remove_sub, "red", "black"),
                         ";'>",
                         subid,
                         "</span>", sep = ""),
         x.label = fct_reorder(x.label, as.character(subid)))
ggplot(data=attention_check_sum,aes(x=x.label,y=accuracy,fill=session_str))+
  geom_col(position=position_dodge2(1))+
  theme(aspect.ratio = 0.3,
        axis.text.x = element_markdown(angle=90),#,colour = ifelse(attention_check_sum$subid%in%remove_sub, "red", "black")
        legend.position = "top")+
  geom_hline(aes(yintercept=0.5))+
  labs(fill="session",title="attention check accuracy")

filter(attention_check_sum,accuracy<0.5)$subid #==min(attention_check_sum$accuracy)
```

Subid "NnGwayWijsWN" attention check accuracy is too low, so removed from analysis
```{r}
remove_sub = c("RcwaTugr8Fiz","FZy8PSATlIm3","SyZeCxfhSm2n","bHAKEOQOX39l")
pilot_data = pilot_data%>%
  filter(ctrl_ept==1&!(subid %in% remove_sub))

range_xy = c(max(pilot_data$stim_x)-min(pilot_data$stim_x),
             max(pilot_data$stim_y)-min(pilot_data$stim_y))

pilot_data = pilot_data%>%
  mutate(expt_map     = factor(expt_map,levels=c(0,1,2,3)),
         expt_maptype = factor(if_else(expt_map%in%c(0,1),"training maps","cross maps"),levels=c("training maps","cross maps")),
         iscenter     = factor(if_else(stim_x*stim_y==0,"center","noncenter"),levels=c("center","noncenter")),
         istraining = factor(istraining,level=c(1,0),labels=c("training","validation+test"))
#         stim_type = ifelse(expt_maptype=="cross maps",
#                            paste(expt_maptype,iscenter,sep="\n"),
#                            paste(expt_maptype,iscenter,sep="\n"))
        )%>%
  mutate(stim_group = factor(stim_group,levels = c("training","validation","test")),
         stim_xO = stim_x,
         stim_yO = stim_y,
         resp_xO = resp_x,
         resp_yO = resp_y,
         ##rescale so that correct location is between -1 and 1
         stim_x = round(2*stim_x/range_xy[1],digits = 3),
         stim_y = round(2*stim_y/range_xy[2],digits = 3),
         distractor_x = round(2*distractor_x/range_xy[1],digits = 3),
         distractor_y = round(2*distractor_y/range_xy[2],digits = 3),
         resp_x = round(2*resp_x/range_xy[1],digits = 3),
         resp_y = round(2*resp_y/range_xy[2],digits = 3),
         stim_attrx = factor(stim_x),
         stim_attry = factor(stim_y),
         stim_attryshape = factor(stim_attry,labels = x_shapes),
         expt_session=ifelse(expt_block>=8*2+4,2,expt_session)
         )%>%
  mutate(session_str=factor(expt_session,levels=c(0,1,2),labels=c("pre-train","refresher","test (no feedback)")))

```

# classify participants according to performance in Treasure Hunt task
```{r filter treasure hunt data}
data = pilot_data%>%
  filter(expt_task==0)

#check if number of trials is correct:
(nsub = length(unique(data$subid))) #= 8
(ntrialpersub = nrow(data)/nsub) # 532 = 8 cycle/map * 2 map * (8+8+8) trial/cycle +  3 refresher block * 2map * 8trial/refresher block + 4*25


data = data%>%
  mutate(resp_dist = sqrt((resp_x-stim_x)^2+(resp_y-stim_y)^2))

re_Assign_msblock = data%>%distinct(subid,expt_map,expt_session,expt_block,.keep_all = T)%>%
  group_by(subid,expt_map,expt_session)%>%
  arrange(expt_block)%>%
  mutate(blocknumber_withinsess = row_number())%>%
  dplyr::select(c("subid","expt_map","expt_session","expt_block","blocknumber_withinsess"))
data = left_join(data,re_Assign_msblock)


```

## calculate llr for each participant and classify learner/generalizer
### llr from fixed non participant specific
```{r calculate llr for each participant}
#load model distribution df
load(file.path(llr_dir,"probDF_data_compo_withlapse.RData"))
cl<- makeCluster(detectCores())
clusterExport(cl=cl,
              varlist = c("data","unique_stimloc","base","prob_df_list"),
              envir=environment())
new_rows <- pblapply(cl = cl,X = seq(1,nrow(data)),FUN = function(j){
  library(dplyr)
  sx = data$stim_x[j]
  sy = data$stim_y[j]
  rx = data$resp_x[j]
  ry = data$resp_y[j]

  ind = filter(unique_stimloc,x == sx & y == sy)$loc_id
  search_df=prob_df_list[[ind]]
  xlb = base[max(which(base<=rx))]
  xub = base[min(which(base>rx))]
  ylb = base[max(which(base<=ry))]
  yub = base[min(which(base>ry))]
  
  new_row = filter(search_df,x<xub & x>=xlb & y<yub & y>=ylb)
  if(nrow(new_row)==0){
    new_row[1, ] <- NA
    new_row = new_row%>%
    mutate(subid = data$subid[j],
           expt_session = data$expt_sess[j],
           expt_block = data$expt_block[j],
           expt_trial = data$expt_trial[j])
  }else{
    new_row = new_row%>%
    mutate(subid  = data$subid[j],
           expt_session = data$expt_sess[j],
           expt_block = data$expt_block[j],
           expt_trial = data$expt_trial[j])
  }
  new_row = new_row%>%
    mutate(binorm_lap = BND_compo_lap)%>%
    mutate(LR_trial = binorm_lap/uniform,
           LRx_trial = UND_x_lap/uniform,
           LRy_trial = UND_y_lap/uniform,)%>%
    mutate(LLR_trial = log(LR_trial),
           LLRx_trial = log(LRx_trial),
           LLRy_trial = log(LRy_trial))%>%
    dplyr::select(c(subid,expt_session,expt_block,expt_trial,LLR_trial,LLRx_trial,LLRy_trial))
  return(new_row)
  })
stopCluster(cl)

a = do.call(rbind,new_rows)

data_with_prob = left_join(data,a)
save(data_with_prob, file = file.path(data_dir,"data_withprob_compo_lapse-0_05.RData"))

data_with_prob = loadRData(file.path(data_dir,"data_withprob_compo_lapse-0_05.RData"))
data_with_prob = data_with_prob%>%
  mutate(error_x = abs(stim_x - resp_x),
         error_y = abs(stim_y - resp_y))%>%
  group_by(subid)%>%
    arrange(stim_group,expt_session,expt_block)%>%
    mutate(trialid_withinstage = row_number(),
           ntrials = n())%>%
  ungroup()
```

<!-- ### llr from participant specific -->
<!-- ```{r calculate llr for each participant} -->
<!-- subdata_list = list() -->
<!-- for (participantid in unique(data_with_prob$subid)){ -->
<!--   #load model distribution df -->
<!--   exp_llr_dir = file.path(data_dir,"participant-specific LLR",fsep="/") -->
<!--   sub_llr_dir = file.path(exp_llr_dir,participantid) -->
<!--   load(file.path(sub_llr_dir,"probDF_data_compo_withlapse.RData",fsep="/")) -->

<!--   subdata = data_with_prob%>%filter(subid==participantid) -->

<!--   cl<- makeCluster(detectCores()) -->
<!--   clusterExport(cl=cl, -->
<!--                 varlist = c("subdata","unique_stimloc","base","prob_df_list"), -->
<!--                 envir=environment()) -->
<!--   new_rows <- pblapply(cl = cl,X = seq(1,nrow(subdata)),FUN = function(j){ -->
<!--     library(dplyr) -->
<!--     sx = subdata$stim_x[j] -->
<!--     sy = subdata$stim_y[j] -->
<!--     em = subdata$expt_map[j] -->
<!--     rx = subdata$resp_x[j] -->
<!--     ry = subdata$resp_y[j] -->

<!--     ind = filter(unique_stimloc,stim_x == sx & stim_y == sy & expt_map == em)$loc_id -->
<!--     search_df=prob_df_list[[ind]] -->
<!--     xlb = base[max(which(base<=rx))] -->
<!--     xub = base[min(which(base>rx))] -->
<!--     ylb = base[max(which(base<=ry))] -->
<!--     yub = base[min(which(base>ry))] -->

<!--     new_row = filter(search_df,x<xub & x>=xlb & y<yub & y>=ylb) -->
<!--     if(nrow(new_row)==0){ -->
<!--       new_row[1, ] <- NA -->
<!--       new_row = new_row%>% -->
<!--       mutate(subid = subdata$subid[j], -->
<!--              expt_session = subdata$expt_session[j], -->
<!--              expt_block = subdata$expt_block[j], -->
<!--              expt_trial = subdata$expt_trial[j]) -->
<!--     }else{ -->
<!--       new_row = new_row%>% -->
<!--       mutate(subid  = subdata$subid[j], -->
<!--              expt_session = subdata$expt_session[j], -->
<!--              expt_block = subdata$expt_block[j], -->
<!--              expt_trial = subdata$expt_trial[j]) -->
<!--     } -->
<!--     new_row = new_row%>% -->
<!--       mutate(binorm_lap = BND_compo_lap)%>% -->
<!--       mutate(LR_trial = binorm_lap/uniform, -->
<!--              LRx_trial = UND_x_lap/uniform, -->
<!--              LRy_trial = UND_y_lap/uniform,)%>% -->
<!--       mutate(pLLR_trial = log(LR_trial), -->
<!--              pLLRx_trial = log(LRx_trial), -->
<!--              pLLRy_trial = log(LRy_trial))%>% -->
<!--       dplyr::select(c(subid,expt_session,expt_block,expt_trial,pLLR_trial,pLLRx_trial,pLLRy_trial)) -->
<!--     return(new_row) -->
<!--     }) -->
<!--   stopCluster(cl) -->

<!--   a = do.call(rbind,new_rows) -->

<!--   subdata = left_join(subdata,a) -->
<!--   subdata_list = append(subdata_list,list(subdata)) -->
<!-- } -->

<!-- data_with_pllr = reduce(subdata_list,rbind) -->
<!--   #loadRData(file.path(data_dir,"data_withprob_compo_lapse-0_05.RData")) -->

<!-- ``` -->

<!-- ```{r} -->
<!-- # use fixed llr for training and pllr for test -->
<!-- data_with_prob_1 = data_with_pllr%>% -->
<!--   mutate(LLR_trial  = ifelse(stim_group=="training",LLR_trial,pLLR_trial), -->
<!--          LLRx_trial = ifelse(stim_group=="training",LLRx_trial,pLLRx_trial), -->
<!--          LLRy_trial = ifelse(stim_group=="training",LLRy_trial,pLLRy_trial)) -->
<!-- data_with_prob_0 = data_with_prob  -->
<!-- data_with_prob = data_with_prob_0  -->
<!-- ``` -->



```{r classify learner}
sub_LLR_data = aggregate_data(data_with_prob,
                              groupbyvars = c("subid","expt_map","stim_group","expt_session","blocknumber_withinsess"),
                              yvars = c("LLR_trial","LLRx_trial","LLRy_trial"),
                              stats = c("mu"),
                              additionalvars = c("expt_coordsys","expt_curricula","expt_session","expt_maptype"))%>%
  change_cols_name(oldnames = c("mu_LLR_trial","mu_LLRx_trial","mu_LLRy_trial"),
                   newnames = c("LLR","LLR_x","LLR_y"))

dividesub = sub_LLR_data%>%
  filter(expt_maptype=="training maps")%>%
  dplyr::select(-c(starts_with("n_")))%>%
  group_by(subid,stim_group,expt_session)%>%
  mutate(nblock = max(blocknumber_withinsess))%>%
  filter(blocknumber_withinsess == nblock)%>%
  aggregate_data(groupbyvars = c("subid","stim_group","expt_session"),
                 yvars = c("LLR"),
                 stats = c("sum"))

#
classify_session = 0
classify_l = "training"
classify_g = "validation"
learnerids = unique(filter(dividesub,expt_session==classify_session&stim_group==classify_l&sum_LLR>=0)$subid)
generalizerids = unique(filter(dividesub,expt_session==classify_session&stim_group==classify_g&sum_LLR>=0)$subid)
(nongeneralizerids = unique(filter(dividesub,expt_session==classify_session&stim_group==classify_g&sum_LLR<0)$subid))
(nonlearnerids = unique(filter(dividesub,expt_session==classify_session&stim_group==classify_l&sum_LLR<0)$subid))

# learnerids = c("6Wgfkt0TDbfN","IaUzcq81FpYy","XeoSBLkhOwc5",
#                "7X9sxTIl0sFc","YBQSartY8cGi", "0x3b1d7RNwtn",
#                "ei39tqQQ2Uoj", "j5qR4VPBKbAD", "4i2wCqKlzfcz",
#                "73ToiYjyUPlD")
#nongeneralizerids = c("6Wgfkt0TDbfN","7X9sxTIl0sFc","zrWMqvmHKVSV","Tf8ODdWcZp2M","4i2wCqKlzfcz")
#generalizerids = c("XeoSBLkhOwc5","YBQSartY8cGi","0x3b1d7RNwtn","ei39tqQQ2Uoj","j5qR4VPBKbAD",
#                   "73ToiYjyUPlD","IaUzcq81FpYy")

data_with_prob = data_with_prob%>%
  mutate(islearner = ifelse(subid%in%learnerids,1,0),
         isgeneralizer = ifelse(subid%in%generalizerids ,1,0))%>%
  mutate(islearner = factor(islearner,levels = c(0,1),labels = c("non-learner","learner")),
         isgeneralizer = factor(isgeneralizer,levels = c(0,1),labels = c("non-generalizer","generalizer")))

sub_LLR_data = sub_LLR_data%>%
  mutate(islearner = ifelse(subid%in%learnerids,1,0),
         isgeneralizer = ifelse(subid%in%generalizerids ,1,0))%>%
  mutate(islearner = factor(islearner,levels = c(0,1),labels = c("non-learner","learner")),
         isgeneralizer = factor(isgeneralizer,levels = c(0,1),labels = c("non-generalizer","generalizer")))
```

```{r count participant type}
nlearners = length(learnerids)
ngeneralizers = length(generalizerids)
nsub = length(unique(sub_LLR_data$subid))
participant_count = sub_LLR_data%>%
  distinct(subid,islearner,isgeneralizer)%>%
  group_by(islearner,isgeneralizer)%>%
  summarise(n = n())
participant_count = participant_count%>%
  mutate(label = paste0(isgeneralizer, "\n n=",n))
participant_count
labelling_func = function(row){
  l = row[1]
  g = row[2]
  return(filter(participant_count,islearner==l&isgeneralizer==g)$label)
}
```

# organize 2AFC data
# 2AFC task{.tabset}

```{r filter 2AFC task data}
fc_df_all = pilot_data%>%
  filter(expt_task==1)%>%
  mutate(distractor_dist = sqrt((distractor_x-stim_x)^2+(distractor_y-stim_y)^2),
         distractor_distx = abs(distractor_x-stim_x),
         distractor_disty = abs(distractor_y-stim_y),
         distractor_relx = distractor_x-stim_x,
         distractor_rely = distractor_y-stim_y,
         )%>%
  mutate(islearner = ifelse(subid%in%learnerids,1,0),
         isgeneralizer = ifelse(subid%in%generalizerids ,1,0))%>%
  mutate(islearner = factor(islearner,levels = c(0,1),labels = c("non-learner","learner")),
         isgeneralizer = factor(isgeneralizer,levels = c(0,1),labels = c("non-generalizer","generalizer")))


re_Assign_blockfc = fc_df_all%>%distinct(subid,expt_map,expt_session,expt_block,.keep_all = T)%>%
  group_by(subid,expt_map,expt_session)%>%
  arrange(expt_block)%>%
  mutate(blocknumber_withinsess = row_number())%>%
  dplyr::select(c("subid","expt_map","expt_session","expt_block","blocknumber_withinsess"))
fc_df_all = left_join(fc_df_all,re_Assign_blockfc)
fc_df_all = fc_df_all%>%
  mutate(resp_correct = resp_choice!=distactorside,
         missed = is.na(resp_correct),
         choosen_x = if_else(resp_correct==1,stim_x,distractor_x),
         choosen_y = if_else(resp_correct==1,stim_y,distractor_y))


## assign location id to each stimuli
find_loc_id = function(datax,datay){
  filter(unique_stimloc,x == datax & y == datay)$ind
}
cl<- makeCluster(detectCores())
clusterExport(cl=cl,
              varlist = c("fc_df_all","unique_stimloc","find_loc_id"),
              envir=environment())
stim_locid <- pblapply(cl = cl,X = seq(1,nrow(fc_df_all)),
                     FUN = function(j){ 
                       library(dplyr)
                       return (find_loc_id(fc_df_all$stim_x[j],fc_df_all$stim_y[j]))}
                     )
distractor_locid <- pblapply(cl = cl,X = seq(1,nrow(fc_df_all)),
                     FUN = function(j){ 
                       library(dplyr)
                       return (find_loc_id(fc_df_all$distractor_x[j],fc_df_all$distractor_y[j]))}
                     )
fc_df_all$stim_locid=stim_locid
fc_df_all$distractor_locid=distractor_locid


```

# debrief

```{r}
debrief_data = read.csv(file.path(data_dir,"debrief_data.csv",fsep="/"))
cluster_data = read.csv(file.path(data_dir,"cluster_data.csv",fsep="/"))
debrief_cluster_data = left_join(cluster_data,debrief_data,by=c("prolificid","subid"))%>%
  filter(!(subid %in% remove_sub))%>%
  mutate(islearner = subid %in% learnerids,
         isgeneralizer = subid %in% generalizerids)%>%
  separate(col = symattr, into = c("symbol_axis", "symbol_axisloc"), sep = "_",remove = FALSE)%>%
  mutate(islearner = factor(islearner,levels = c(FALSE,TRUE),labels = c("non-learner","learner")),
         isgeneralizer = factor(isgeneralizer,levels = c(FALSE,TRUE),labels = c("non-generalizer","generalizer")))
```

# save data
```{r}
save(data_with_prob,fc_df_all,debrief_cluster_data,learnerids,generalizerids,
     labelling_func,participant_count,
     file = file.path(data_dir,"allexpdata_compo_lapse-0_01.RData"))
```

