---
title: "Data from Pilot M1V1"
output: html_document
date: "2024-03-12"
---

```{r setup, include=FALSE}

rm(list = ls())
knitr::opts_chunk$set(error = FALSE,echo=FALSE, message=FALSE, warning=FALSE,fig.height = 9)

rm(list = ls())
project_dir = rstudioapi::getActiveProject();
src_dir = file.path(project_dir, "src/R", fsep="/")
llr_dir = file.path(project_dir, "src/LLR", fsep="/")

data_dir = file.path(project_dir, "data","Exp2_pilots","1_M1_v1", fsep="/")
result_dir = file.path(project_dir, "results","Exp2_pilots","1_M1_v1", fsep="/")


source(file.path(src_dir,"envSetup.R",fsep="/"), local = knitr::knit_global())
source(file.path(src_dir,"funcDef.R",fsep="/"), local = knitr::knit_global())
source(file.path(src_dir,"setPlotDefault.R",fsep="/"), local = knitr::knit_global())
```

# Attention Check
Plot attention check results and see if any need to be excluded from analyses
```{r}
pilot_data = read.csv(file.path(data_dir,"task_data.csv",fsep="/"))
attention_check_data = pilot_data%>%
  filter(ctrl_ept==0)
attention_check_sum = attention_check_data%>%
  aggregate_data(groupbyvars=c("subid","expt_session"),
                 yvars="resp_correct",
                 stats = c("sum","n","mu"))%>%
  change_cols_name(oldnames=c("sum_resp_correct","n_resp_correct","mu_resp_correct"),
                   newnames=c("n_correct","n_totaltrials","accuracy"))
attention_check_sum = attention_check_sum%>%
  mutate(session_str = factor(expt_session,
                              levels=c(0,1),
                              labels=c(sprintf("session1 (%d trials)",unique(filter(attention_check_sum,expt_session==0)$n_totaltrials)),
                                       sprintf("session1 (%d trials)",unique(filter(attention_check_sum,expt_session==1)$n_totaltrials))
                                       )
                              ))
  


ggplot(data=attention_check_sum,aes(x=subid,y=accuracy,fill=session_str))+
  geom_col(position=position_dodge2(1))+
  theme(aspect.ratio = 0.6,axis.text.x = element_text(angle=90),legend.position = "top")+
  labs(fill="session",title="attention check accuracy")

filter(attention_check_sum,accuracy==min(attention_check_sum$accuracy))$subid
```

Subid "lKo186FW3Hk0" attention check accuracy is too low, so removed from analysis
```{r}
remove_sub = c("lKo186FW3Hk0")
pilot_data = pilot_data%>%
  filter(ctrl_ept==1&!(subid %in% remove_sub))%>%
  mutate(session_str=factor(expt_session,levels=c(0,1),labels=c("session 1","session2")))

range_xy = c(max(pilot_data$stim_x)-min(pilot_data$stim_x),
             max(pilot_data$stim_y)-min(pilot_data$stim_y))

pilot_data = pilot_data%>%
  mutate(stim_group = factor(stim_group,levels = c("training","validation","test")),
         stim_xO = stim_x,
         stim_yO = stim_y,
         resp_xO = resp_x,
         resp_yO = resp_y,
         ##rescale so that correct location is between -1 and 1
         stim_x = round(2*stim_x/range_xy[1],digits = 3),
         stim_y = round(2*stim_y/range_xy[2],digits = 3),
         distractor_x = round(2*distractor_x/range_xy[1],digits = 3),
         distractor_y = round(2*distractor_y/range_xy[2],digits = 3),
         resp_x = round(2*resp_x/range_xy[1],digits = 3),
         resp_y = round(2*resp_y/range_xy[2],digits = 3),
         stim_attrx = factor(stim_x),
         stim_attry = factor(stim_y),
         stim_attryshape = factor(stim_attry,labels = x_shapes),
         )

```


# Treasure Hunt task
```{r filter treasure hunt data}
data = pilot_data%>%
  filter(expt_task==0)

#check if number of trials is correct:
#nsub = length(unique(respdata$subid)) = ?
#ntrialpersub = nrow(respdata)/nsub = ?


data = data%>%
  mutate(resp_dist = sqrt((resp_x-stim_x)^2+(resp_y-stim_y)^2))

re_Assign_block = data%>%distinct(subid,expt_session,expt_block,.keep_all = T)%>%
  group_by(subid,expt_session)%>%
  arrange(expt_block)%>%
  mutate(blocknumber_withinsess = row_number())%>%
  dplyr::select(c("subid","expt_session","expt_block","blocknumber_withinsess"))
data = left_join(data,re_Assign_block)

```

## calculate llr for each participant and classify learner/generalizer
```{r load model distribution df}
load(file.path(llr_dir,"probDF_data_compo_withlapse.RData"))
```


```{r calculate llr for each participant}
tryCatch(
  expr = {
    data_with_prob = loadRData(file.path(data_dir,"data_withprob_compo_lapse-0_01.RData"))
  },
  error = function(e){
    cl<- makeCluster(detectCores())
    clusterExport(cl=cl,
                  varlist = c("data","unique_stimloc","base","prob_df_list"),
                  envir=environment())
    new_rows <- pblapply(cl = cl,X = seq(1,nrow(data)),FUN = function(j){
      library(dplyr)
      sx = data$stim_x[j]
      sy = data$stim_y[j]
      rx = data$resp_x[j]
      ry = data$resp_y[j]

      ind = filter(unique_stimloc,x == sx & y == sy)$loc_id
      search_df=prob_df_list[[ind]]
      xlb = base[max(which(base<=rx))]
      xub = base[min(which(base>rx))]
      ylb = base[max(which(base<=ry))]
      yub = base[min(which(base>ry))]
      
      new_row = filter(search_df,x<xub & x>=xlb & y<yub & y>=ylb)
      if(nrow(new_row)==0){
        new_row[1, ] <- NA
        new_row = new_row%>%
        mutate(resp_x = rx, resp_y = ry,
               subid = data$subid[j],
               expt_session = data$expt_sess[j],
               expt_block = data$expt_block[j],
               expt_trial = data$expt_trial[j])
      }else{
        new_row = new_row%>%
        mutate(resp_x = rx, resp_y = ry,
               subid  = data$subid[j],
               expt_session = data$expt_sess[j],
               expt_block = data$expt_block[j],
               expt_trial = data$expt_trial[j])
      }
      
      return(new_row)
      })
    stopCluster(cl)
    
    a = do.call(rbind,new_rows)
    
    data_with_prob = left_join(data,a)
    save(data_with_prob, file = file.path(data_dir,"data_withprob_compo_lapse-0_01.RData"))
  }
)

data_with_prob = loadRData(file.path(data_dir,"data_withprob_compo_lapse-0_01.RData"))

```



```{r classify learner}
data_with_prob = data_with_prob%>%
  mutate(error_x = abs(stim_x - resp_x),
         error_y = abs(stim_y - resp_y))%>%
  mutate(binorm_lap = BND_compo_lap)%>%
  mutate(LR_trial = binorm_lap/uniform,
         LRx_trial = UND_x_lap/uniform,
         LRy_trial = UND_y_lap/uniform,)%>%
  mutate(LLR_trial = log(LR_trial),
         LLRx_trial = log(LRx_trial),
         LLRy_trial = log(LRy_trial))%>%
  group_by(subid)%>%
    arrange(stim_group,expt_session,expt_block)%>%
    mutate(trialid_withinstage = row_number(),
           ntrials = n())%>%
  ungroup()

sub_LLR_data = aggregate_data(data_with_prob,
                              groupbyvars = c("subid","stim_group","expt_session","blocknumber_withinsess"),
                              yvars = c("LLR_trial","LLRx_trial","LLRy_trial"),
                              stats = c("mu"),
                              additionalvars = c("expt_coordsys","expt_curricula","expt_session"))%>%
  change_cols_name(oldnames = c("mu_LLR_trial","mu_LLRx_trial","mu_LLRy_trial"),
                   newnames = c("LLR","LLR_x","LLR_y"))

dividesub = sub_LLR_data%>%
  dplyr::select(-c(starts_with("n_")))%>%
  group_by(subid,stim_group)%>%
  mutate(nblock = max(blocknumber_withinsess))%>%
  aggregate_data(groupbyvars = c("subid","stim_group","expt_session"),
                 yvars = c("LLR"),
                 stats = c("sum"))

learnerids = unique(filter(dividesub,expt_session==1&stim_group=="training"&sum_LLR>=0)$subid)
generalizerids = unique(filter(dividesub,expt_session==1&stim_group=="validation"&sum_LLR>=0)$subid)
(nonlearnerids = unique(filter(dividesub,expt_session==1&stim_group=="training"&sum_LLR<0)$subid))
(nongeneralizerids = unique(filter(dividesub,expt_session==1&stim_group=="validation"&sum_LLR<0)$subid))

data_with_prob = data_with_prob%>%
  mutate(islearner = ifelse(subid%in%learnerids,1,0),
         isgeneralizer = ifelse(subid%in%generalizerids ,1,0))%>%
  mutate(islearner = factor(islearner,levels = c(0,1),labels = c("non-learner","learner")),
         isgeneralizer = factor(isgeneralizer,levels = c(0,1),labels = c("non-generalizer","generalizer")))

sub_LLR_data = sub_LLR_data%>%
  mutate(islearner = ifelse(subid%in%learnerids,1,0),
         isgeneralizer = ifelse(subid%in%generalizerids ,1,0))%>%
  mutate(islearner = factor(islearner,levels = c(0,1),labels = c("non-learner","learner")),
         isgeneralizer = factor(isgeneralizer,levels = c(0,1),labels = c("non-generalizer","generalizer")))
```
```{r count participant type}
nlearners = length(learnerids)
ngeneralizers = length(generalizerids)
nsub = length(unique(sub_LLR_data$subid))
participant_count = sub_LLR_data%>%
  distinct(subid,islearner,isgeneralizer)%>%
  group_by(islearner,isgeneralizer)%>%
  summarise(n = n())
participant_count = participant_count%>%
  mutate(label = paste0(isgeneralizer, "\n n=",n))
participant_count
labelling_func = function(row){
  l = row[1]
  g = row[2]
  return(filter(participant_count,islearner==l&isgeneralizer==g)$label)
}
```


## Behavioural performance of learner/generalizer in treasure hunt task{.tabset}
```{r treasurehunt block average}
blockdata_sub = aggregate_data(data_with_prob,
                           yvars = c("resp_dist","LLR_trial","LLRx_trial","LLRy_trial","error_x","error_y"),
                           groupbyvars = c("subid","stim_group","expt_session","blocknumber_withinsess"),
                           stats = c("mu"),
                           additionalvars = c("islearner","isgeneralizer","session_str"))%>%
  change_cols_name(oldnames = c("mu_LLR_trial","mu_LLRx_trial","mu_LLRy_trial",
                                "mu_resp_dist","mu_error_x","mu_error_y"),
                   newnames = c("LLR","LLR_x","LLR_y",
                                "distance","errorx","errory"))


blockdata_sum = aggregate_data(blockdata_sub,
                           yvars = c("distance","LLR","LLR_x","LLR_y","errorx","errory"),
                           groupbyvars = c("islearner","isgeneralizer","stim_group",
                                           "expt_session","blocknumber_withinsess"),
                           stats = c("mu","se","n"),
                           additionalvars = c("session_str"))
```



### rescaled distance to goal
```{r rescaled distance to goal}
# with data count
blockdata_sub$generalizer_label =
apply(blockdata_sub[ , c("islearner","isgeneralizer")], 1, labelling_func)
blockdata_sum$generalizer_label =
apply(blockdata_sum[ , c("islearner","isgeneralizer")], 1, labelling_func)
(p = blockdata_sub%>%
  ggplot(aes(x=blocknumber_withinsess,y=distance,fill=stim_group,color=stim_group))+
  geom_point(alpha = 0.3,size = 2,stroke=0)+
  geom_line(data = blockdata_sum,
            aes(x=blocknumber_withinsess,y=mu_distance))+
  geom_errorbar(data = blockdata_sum,
                aes(x=blocknumber_withinsess,
                    y = mu_distance,
                    ymin = mu_distance - se_distance,
                    ymax = mu_distance + se_distance),
                width=0.4)+
  facet_nested(cols =vars(session_str),
               rows = vars(islearner,generalizer_label),
               scales = "free_x",space = "free_x")+
  scale_x_continuous(breaks = seq(1,36,1))+
  guides(fill = "none")+
  labs(x="block number",y="mean distance to goal (a.u.) rescaled",color = "stim_group",
       title = "Distance to correct location")+
  theme(aspect.ratio = 8,legend.position = "top"))

ggsave(file.path(result_dir,paste0('rescaled_distance_classified','.png')),plot = p,device = 'png',width = 15,height = 8)
```

### mean LLR
```{r}
#withdatacount
(p = blockdata_sub%>%
  ggplot(aes(x=blocknumber_withinsess,y=LLR,fill=stim_group,color=stim_group))+
  geom_point(alpha = 0.3,size = 2,stroke=0)+
  geom_line(data = blockdata_sum,
            aes(x=blocknumber_withinsess,y=mu_LLR))+
  geom_errorbar(data = blockdata_sum,
                aes(x=blocknumber_withinsess,
                    y = mu_LLR,
                    ymin = mu_LLR - se_LLR,
                    ymax = mu_LLR + se_LLR),
                width=0.4)+
  facet_nested(cols =vars(session_str),
               rows = vars(islearner,generalizer_label),
               scales = "free_x",space = "free_x")+
  scale_x_continuous(breaks = seq(1,12,1))+
  guides(fill = "none")+
  labs(x="block number",y="mean LLR",color = "stim group",
       title = "Log-Likelihood Ratio")+
  theme(aspect.ratio = 8,legend.position = "top"))

ggsave(file.path(result_dir,paste0('LLR_classified','.png')),plot = p,device = 'png',width = 15,height = 8)
```

### Individual response map
<!-- ### with label -->
<!-- ```{r} -->
<!-- for (pid in unique(data_with_prob$subid)){ -->
<!--   current_data = filter(data_with_prob,subid == pid) -->
<!--   plot_name = paste0(pid,"\n", -->
<!--                     ifelse(pid %in% learnerids,"learner","nonlearner"), -->
<!--                     " - ", -->
<!--                     ifelse(pid %in% generalizerids,"generalizer","nongeneralizer")) -->

<!--   n_refresher=6 -->
<!--   n_trainingcycle=12 -->
<!--   nb_percyc = 3 -->
<!--   n_test = 4 -->
<!--   layoutmat = matrix(c(## first three rows are training cycles -->
<!--                        seq(1,n_trainingcycle*nb_percyc,by=nb_percyc), -->
<!--                        seq(2,n_trainingcycle*nb_percyc,by=nb_percyc), -->
<!--                        seq(3,n_trainingcycle*nb_percyc,by=nb_percyc), -->
<!--                        ## refresher -->
<!--                        seq(n_trainingcycle*nb_percyc+1,n_trainingcycle*nb_percyc+n_refresher,by=1), NA,NA, -->
<!--                        ## test -->
<!--                        seq(n_trainingcycle*nb_percyc+n_refresher+2, -->
<!--                            n_trainingcycle*nb_percyc+n_refresher+n_test+1),  -->
<!--                        rep(NA,n_trainingcycle-n_test-n_refresher-2) -->
<!--                        ), -->
<!--                      4, n_trainingcycle, byrow = TRUE) -->
<!--   (p = current_data%>% -->
<!--     ggplot(aes(x=resp_x, y = resp_y, color = stim_attrx,fill = stim_attrx))+ -->
<!--     facet_manual(vars(session_str,blocknumber_withinsess),design = layoutmat,strip = strip_nested())+ -->
<!--     geom_point(aes(shape = stim_attry),size=3.5,alpha=0.6)+ -->
<!--     scale_color_manual(values = y_colors,aesthetics = c("color","fill"))+ -->
<!--     scale_shape_manual(values = x_shapes)+ -->
<!--     guides(fill = "none")+ -->
<!--     labs(title = plot_name,color = "true x",shape = "true y", x = "response x", y = "response y")+ -->
<!--     theme(legend.position = "top",aspect.ratio = 1)) -->
<!--   ggsave(file.path(result_dir,'individualmaps',"participant_map_rescaled",paste0(pid,'.png')),plot = p,device = 'png',width = 15,height = 9) -->
<!-- } -->
<!-- ``` -->

```{r 2D + 1D LLR}
for (pid in unique(filter(data_with_prob)$subid)){
  current_data = filter(data_with_prob,subid == pid)%>%
    mutate(stim_attrx = factor(stim_attrx),
           stim_attry = factor(stim_attry),
           islearner = factor(islearner,levels = c(0,1),labels = c("non-learner","learner")),
           isgeneralizer = factor(isgeneralizer,levels = c(0,1),labels = c("non-generalizer","generalizer")))
  current_data_sum = aggregate_data(current_data,
                                    yvars = c("resp_dist","LLR_trial","LLRx_trial","LLRy_trial","error_x","error_y"),
                                    groupbyvars = c("subid","expt_session","blocknumber_withinsess"),
                                    stats = c("mu"),
                                    additionalvars = c("islearner","isgeneralizer","session_str"))%>%
                    change_cols_name(oldnames = c("mu_LLR_trial","mu_LLRx_trial","mu_LLRy_trial",
                                                  "mu_resp_dist","mu_error_x","mu_error_y"),
                                     newnames = c("LLR","LLR_x","LLR_y",
                                                  "distance","errorx","errory"))%>%
                    mutate(islearner = factor(islearner,levels = c(0,1),labels = c("non-learner","learner")),
                           isgeneralizer = factor(isgeneralizer,levels = c(0,1),labels = c("non-generalizer","generalizer")))
  
  
  plot_name = paste(pid,unique(current_data$islearner),unique(current_data$isgeneralizer))
  n_refresher=6
  n_trainingcycle=12
  nb_percyc = 3
  n_test = 4
  layoutmat = matrix(c(## first three rows are training cycles
                       seq(1,n_trainingcycle*nb_percyc,by=nb_percyc),
                       seq(2,n_trainingcycle*nb_percyc,by=nb_percyc),
                       seq(3,n_trainingcycle*nb_percyc,by=nb_percyc),
                       ## refresher
                       seq(n_trainingcycle*nb_percyc+1,n_trainingcycle*nb_percyc+n_refresher,by=1), NA,NA,
                       ## test
                       seq(n_trainingcycle*nb_percyc+n_refresher+2,
                           n_trainingcycle*nb_percyc+n_refresher+n_test+1), 
                       rep(NA,n_trainingcycle-n_test-n_refresher-2)
                       ),
                     4, n_trainingcycle, byrow = TRUE)
  (p = current_data%>%
    ggplot(aes(x=resp_x, y = resp_y))+
    facet_manual(vars(session_str,blocknumber_withinsess),design = layoutmat,strip = strip_nested())+
    geom_point(aes(shape = stim_attry, color = stim_attrx,fill = stim_attrx),size=3.5,alpha=0.7)+
    geom_text(data = current_data_sum,size = 3,
            aes(x=0.1,y=2,label = sprintf("2D LLR = %s", formatC(LLR, digits = 2))))+
    geom_text(data = current_data_sum,size = 3,
              aes(x=0.1,y=1.6,
                  label = sprintf("1D LLR(x,y): [%s, %s]",
                                  formatC(LLR_x, digits = 2),
                                  formatC(LLR_y, digits = 2))))+
    scale_color_manual(values = y_colors,aesthetics = c("color","fill"))+
    scale_shape_manual(values = x_shapes)+
    guides(fill = "none")+
    labs(title = plot_name,
         color = "x feature",shape = "y feature", x = "x", y = "y")+
    theme(legend.position = "top"))
  ggsave(file.path(result_dir,'individualmaps',"participant_map_with1dLLR",paste0(pid,'.png')),plot = p,width = 16,height = 9)
  
}
```

### average response map
```{r}
generalize_js = c("non-generalizer","generalizer")
learn_ks = c("non-learner","learner")
for (j in c(0,1)){
  for (k in c(0,1)){
    ave_resp_map_df = data_with_prob %>%
    filter(isgeneralizer==j,islearner==k)%>%
    aggregate_data(
      yvars = c("resp_x","resp_y"),
      groupbyvars = c("islearner","isgeneralizer","expt_session","blocknumber_withinsess","stim_id"),
      stats = c("mu"),
      additionalvars = c("expt_block","session_str","stim_x","stim_y","stim_attrx","stim_attry")
    )%>%
    change_cols_name(oldnames = c("mu_resp_x","mu_resp_y"),
                     newnames = c("resp_x", "resp_y"))%>%
    mutate(stim_attrx = factor(stim_attrx),
             stim_attry = factor(stim_attry))
  
    if (nrow(ave_resp_map_df)>0){
      n_refresher=6
      n_trainingcycle=12
      nb_percyc = 3
      n_test = 4
      layoutmat = matrix(c(## first three rows are training cycles
                           seq(1,n_trainingcycle*nb_percyc,by=nb_percyc),
                           seq(2,n_trainingcycle*nb_percyc,by=nb_percyc),
                           seq(3,n_trainingcycle*nb_percyc,by=nb_percyc),
                           ## refresher
                           seq(n_trainingcycle*nb_percyc+1,n_trainingcycle*nb_percyc+n_refresher,by=1), NA,NA,
                           ## test
                           seq(n_trainingcycle*nb_percyc+n_refresher+2,
                               n_trainingcycle*nb_percyc+n_refresher+n_test+1), 
                           rep(NA,n_trainingcycle-n_test-n_refresher-2)
                           ),
                         4, n_trainingcycle, byrow = TRUE)
      (p = ave_resp_map_df%>%
        ggplot(aes(x=resp_x, y = resp_y))+
        facet_manual(vars(session_str,blocknumber_withinsess),design = layoutmat,strip = strip_nested())+
        geom_point(aes(color = stim_attry,fill = stim_attry,shape = stim_attrx),size = 3)+
        scale_color_manual(values = y_colors,aesthetics = c("color","fill"))+
        scale_shape_manual(values = x_shapes)+
        guides(fill = "none")+
        labs(title =paste0("average response map: ", learn_ks[k+1],'_',generalize_js[j+1]),
             color = "y feature",shape = "x feature", x = "x", y = "y")+
        theme(legend.position = "top"))
      ggsave(file.path(result_dir,'individualmaps',"averagemaps",
                       paste0(learn_ks[k+1],'_',generalize_js[j+1],'.png')),plot = p,width = 16,height = 9)
    }
  
  }
}

```




# 2AFC task{.tabset}

```{r filter 2AFC task data}
fc_df_all = pilot_data%>%
  filter(expt_task==1)%>%
  mutate(distractor_dist = sqrt((distractor_x-stim_x)^2+(distractor_y-stim_y)^2),
         distractor_distx = abs(distractor_x-stim_x),
         distractor_disty = abs(distractor_y-stim_y),
         distractor_relx = distractor_x-stim_x,
         distractor_rely = distractor_y-stim_y,
         )%>%
  mutate(islearner = ifelse(subid%in%learnerids,1,0),
         isgeneralizer = ifelse(subid%in%generalizerids ,1,0))

re_Assign_blockfc = fc_df_all%>%distinct(subid,expt_session,expt_block,.keep_all = T)%>%
  group_by(subid,expt_session)%>%
  arrange(expt_block)%>%
  mutate(blocknumber_withinsess = row_number())%>%
  dplyr::select(c("subid","expt_session","expt_block","blocknumber_withinsess"))
fc_df_all = left_join(fc_df_all,re_Assign_blockfc)
fc_df_all = fc_df_all%>%
  mutate(resp_correct = resp_choice!=distactorside,
         stage = factor(stim_group,levels = c("training","validation","test")),
         session_str = factor(expt_session, levels = c(0,1),labels=c("s1","s2")),
         missed = is.na(resp_correct),
         istraining = factor(istraining,level=c(1,0),labels=c("training","validation+test")),
         choosen_x = if_else(resp_correct==1,stim_x,distractor_x),
         choosen_y = if_else(resp_correct==1,stim_y,distractor_y))


## assign location id to each stimuli
find_loc_id = function(datax,datay){
  filter(unique_stimloc,x == datax & y == datay)$ind
}
cl<- makeCluster(detectCores())
clusterExport(cl=cl,
              varlist = c("fc_df_all","unique_stimloc","find_loc_id"),
              envir=environment())
stim_locid <- pblapply(cl = cl,X = seq(1,nrow(fc_df_all)),
                     FUN = function(j){ 
                       library(dplyr)
                       return (find_loc_id(fc_df_all$stim_x[j],fc_df_all$stim_y[j]))}
                     )
distractor_locid <- pblapply(cl = cl,X = seq(1,nrow(fc_df_all)),
                     FUN = function(j){ 
                       library(dplyr)
                       return (find_loc_id(fc_df_all$distractor_x[j],fc_df_all$distractor_y[j]))}
                     )
fc_df_all$stim_locid=stim_locid
fc_df_all$distractor_locid=distractor_locid


```

```{r}

fc_df_missedtrial_sub = fc_df_all%>%
  aggregate_data(yvars = c("missed"),
                 groupbyvars = c("subid","stim_group","expt_session","expt_block"),
                           stats = c("mu"),
                           additionalvars = c("blocknumber_withinsess","session_str","islearner","isgeneralizer"))%>%
  change_cols_name("mu_missed","missed")

fc_df_missedtrial_sumblock = fc_df_missedtrial_sub%>%
  aggregate_data(yvars = c("missed"),
                 groupbyvars = c("islearner","isgeneralizer","stim_group","expt_session","expt_block"),
                           stats = c("mu","se"),
                           additionalvars = c("blocknumber_withinsess","session_str","islearner","isgeneralizer"))

ggplot(data=fc_df_missedtrial_sumblock,aes(x=blocknumber_withinsess,y=mu_missed,fill=stim_group,color=stim_group))+
  geom_point(data=fc_df_missedtrial_sub,aes(x=blocknumber_withinsess,y=missed),alpha = 0.3,size = 2,stroke=0)+
  geom_line()+
  geom_errorbar(aes(ymin=mu_missed-se_missed,
                    ymax=mu_missed+se_missed),
                width=0.4)+
  facet_nested(cols = vars(session_str),
               rows = vars(islearner,isgeneralizer),
               scales = "free_x",space = "free_x")+
  scale_x_continuous(breaks = seq(1,12,1))+
  guides(fill = "none")+
  labs(x="block number",y="mean missed",color = "stim group",
       title = "# of missed trials")+
  theme(aspect.ratio = 8,legend.position = "top")

fc_df_missedtrial_sumexp = fc_df_missedtrial_sub%>%
  aggregate_data(yvars = c("missed"),
                 groupbyvars = c("islearner","isgeneralizer","subid","stim_group"),
                           stats = c("mu"))

average_missed_percentage = sum(is.na(fc_df_all$resp_correct))/nrow(fc_df_all)
ggplot(data=fc_df_missedtrial_sumexp,aes(x=subid,y=mu_missed,fill=stim_group,color=stim_group))+
  geom_col(position=position_dodge2(1))+
  #facet_nested(cols = vars(islearner,isgeneralizer))+
  geom_hline(yintercept=average_missed_percentage,show.legend=FALSE)+
  geom_text(aes(color=NULL,fill=NULL,
                x=3.5, y= 0.2,
                label = sprintf("Average missed:  %.1f%s",average_missed_percentage*100,"%")),
            show.legend = FALSE)+
  scale_y_continuous(labels = function(x){sprintf("%.1f%s",x*100,"%")})+
  labs(y="percentage of missed trials in total (%)")+
  theme(axis.text.x = element_text(angle=90))
  
fc_df = filter(fc_df_all,missed==0)

```


## Choice Accuracy and RT
```{r}
blockfcdata_sub = aggregate_data(fc_df,
                           yvars = c("resp_correct","resp_rt","distractor_dist"),
                           groupbyvars = c("subid","stim_group","expt_session","expt_block"),
                           stats = c("mu"),
                           additionalvars = c("blocknumber_withinsess","session_str","islearner","isgeneralizer"))%>%
  change_cols_name(oldnames = c("mu_resp_correct","mu_resp_rt","mu_distractor_dist"),
                   newnames = c("blockacc","blockrt","blockdist"))%>%
  mutate(islearner = factor(islearner,levels = c(0,1),labels = c("non-learner","learner")),
         isgeneralizer = factor(isgeneralizer,levels = c(0,1),labels = c("non-generalizer","generalizer")))

blockfcdata_sum = aggregate_data(blockfcdata_sub,
                           yvars = c("blockacc","blockrt","blockdist"),
                           groupbyvars = c("expt_session","islearner","isgeneralizer","stim_group","expt_block"),
                           additionalvars = c("session_str","blocknumber_withinsess"),
                           stats = c("mu","se"))
```

### Accuracy
```{r}
(p=
   ggplot(data = blockfcdata_sum,
       aes(x=blocknumber_withinsess,y=mu_blockacc,fill=stim_group,color=stim_group))+
  facet_nested(rows=vars(islearner,isgeneralizer),scales = "free_x",space = "free_x")+
  geom_errorbar(aes(ymin = mu_blockacc - se_blockacc,
                    ymax = mu_blockacc + se_blockacc),
                width=0.4,
                position = position_dodge(width=0.5))+
  geom_point(position = position_dodge(width=0.5))+ 
  geom_line(position = position_dodge(width=0.5))+
  geom_point(data=blockfcdata_sub,aes(x=blocknumber_withinsess,y=blockacc),
             alpha = 0.3,size = 2,stroke=0,
             position = position_dodge(width=0.5))+
  labs(x="block number",y="block acc",color = "stim group",
       title = "Choice Accuracy")+
  guides(fill = "none")+
  theme(aspect.ratio = 5,legend.position = "top"))

ggsave(file.path(result_dir,paste0('blockacc_withsess','.png')),plot = p,device = 'png',width = 15,height = 7)
```
```{r}
# set test as reference level for stim group
fc_df <- within(fc_df, stim_group <- relevel(stim_group, ref = "test"))
# set test as reference level for isgeneralizer
fc_df$isgeneralizer = factor(fc_df$isgeneralizer,levels=c(0,1),labels=c("nonGeneralizer","Generalizer"))
fc_df <- within(fc_df, isgeneralizer <- relevel(isgeneralizer, ref = "nonGeneralizer"))
```


```{r}
model = glmer(resp_correct~isgeneralizer*distractor_dist+isgeneralizer*stim_group+blocknumber_withinsess + (1 |subid),
              data=fc_df,family = binomial)
export_summs(model,error_format = "[{conf.low}, {conf.high}]")
```

### RT

```{r}
(p=
   ggplot(data = blockfcdata_sum,
       aes(x=blocknumber_withinsess,y=mu_blockrt,fill=stim_group,color=stim_group))+
  facet_nested(rows=vars(islearner,isgeneralizer),scales = "free_x",space = "free_x")+
  geom_errorbar(aes(ymin = mu_blockrt - se_blockrt,
                    ymax = mu_blockrt + se_blockrt),
                width=0.4,
                position = position_dodge(width=0.5))+
  geom_point(position = position_dodge(width=0.5))+ 
  geom_line(position = position_dodge(width=0.5))+
  geom_point(data=blockfcdata_sub,aes(x=blocknumber_withinsess,y=blockrt,group=subid),
             alpha = 0.3,size = 2,stroke=0,
             position = position_dodge(width=0.5))+
  scale_y_continuous(breaks=c(0,200,400,600,800,1000))+
  labs(x="block number",y="block rt (ms)",color = "stim group",
       title = "Choice RT")+
   guides(fill = "none")+
  theme(aspect.ratio = 5,legend.position = "top"))

ggsave(file.path(result_dir,paste0('blockrt_withsess','.png')),plot = p,device = 'png',width = 15,height = 7)
```

```{r}
(p=
   ggplot(data = blockfcdata_sum,
       aes(x=blocknumber_withinsess,y=mu_blockdist,fill=stim_group,color=stim_group))+
  facet_nested(rows=vars(islearner,isgeneralizer),scales = "free_x",space = "free_x")+
  geom_errorbar(aes(ymin = mu_blockdist - se_blockdist,
                    ymax = mu_blockdist + se_blockdist),
                width=0.4,
                position = position_dodge(width=0.5))+
  geom_point(position = position_dodge(width=0.5))+ 
  geom_line(position = position_dodge(width=0.5))+
  geom_point(data=blockfcdata_sub,aes(x=blocknumber_withinsess,y=blockdist,group=subid),
             alpha = 0.3,size = 2,stroke=0,
             position = position_dodge(width=0.5))+
  labs(x="block number",y="block dist",color = "stim group",
       title = "Block difficulty level (average distractor distance to goal)")+
   guides(fill = "none")+
  theme(aspect.ratio = 5,legend.position = "top"))

ggsave(file.path(result_dir,paste0('blockdist_withsess','.png')),plot = p,device = 'png',width = 15,height = 7)
```


## ERROR PATTERN

```{r}
fc_df = fc_df %>%
  mutate(choosen_locid = if_else(resp_correct==1,stim_locid,distractor_locid))


```

### Relative location of errors
plot each participants error location with respect to the correct location. Are they more likely to make an error when it is within the same row/col? etc

First we plot the totoal number of errors at each relative location
```{r}
fcdf_relloc_nerr = fc_df%>%
  filter(resp_correct==0)%>%
    aggregate_data(groupbyvars = c("subid","stim_id","distractor_relx","distractor_rely"),
                   yvars = c("expt_index"),
                   stats =c("n"),
                   additionalvars = c("isgeneralizer","islearner","istraining"))%>%
    change_cols_name(oldnames = "n_expt_index","n_errors")%>%
  aggregate_data(groupbyvars = c("subid","istraining","distractor_relx","distractor_rely"),
                   yvars = c("n_errors"),
                   stats =c("n"),
                   additionalvars = c("isgeneralizer","islearner"))%>%
  mutate(islearner = factor(islearner,levels = c(0,1),labels = c("non-learner","learner")),
         isgeneralizer = factor(isgeneralizer,levels = c(0,1),labels = c("non-generalizer","generalizer")))
ggplot(fcdf_relloc_nerr,aes(x=distractor_relx,y=distractor_rely,fill=n_n_errors))+
    geom_tile(linewidth=0.8,width=0.4,height=0.4)+
  scale_colour_viridis_c(aesthetics = c("fill"))+
  #scale_linewidth_manual(values=c(1,0))+
  facet_nested(rows = vars(istraining),cols=vars(islearner,isgeneralizer,subid))+
  theme(legend.position = "top",legend.direction = "horizontal")
```

Then we plot the percentage of errors at each relative location:
```{r}
fcdf_relloc_perr = fc_df%>%
  ## calculate for each participant, at each stimuli, how many trials have response
  group_by(subid,stim_id)%>%
  mutate(n_2afctrials_withresp=n())%>%
  ungroup()%>%
  ### calculate the number of errors for each participant, at each stimuli 
  filter(resp_correct==0)%>%
  group_by(subid,stim_id)%>%
  mutate(n_total2afcerr=n())%>%
  ungroup()%>%
  
  ### calculate the percentange of errors for each stimuli at different relative locations 
    aggregate_data(groupbyvars = c("subid","stim_id","distractor_relx","distractor_rely"),
                   yvars = c("expt_index"),
                   stats =c("n"),
                   additionalvars = c("isgeneralizer","islearner","istraining","n_2afctrials_withresp","n_total2afcerr"))%>%
    change_cols_name(oldnames = "n_expt_index","n_errors")%>%
    mutate(p_error = n_errors/n_total2afcerr)%>%
  
  ### calculate the average percentage of errors at different relative locations for different  stimuli type: training vs validation
  aggregate_data(groupbyvars = c("subid","istraining","distractor_relx","distractor_rely"),
                   yvars = c("p_error"),
                   stats =c("mu"),
                   additionalvars = c("isgeneralizer","islearner"))%>%
  mutate(islearner = factor(islearner,levels = c(0,1),labels = c("non-learner","learner")),
         isgeneralizer = factor(isgeneralizer,levels = c(0,1),labels = c("non-generalizer","generalizer")))
ggplot(fcdf_relloc_perr,aes(x=distractor_relx,y=distractor_rely,fill=mu_p_error))+
    geom_tile(linewidth=0.8,width=0.4,height=0.4)+
  scale_colour_viridis_c(aesthetics = c("colour", "fill"))+
  #scale_linewidth_manual(values=c(1,0))+
  facet_nested(rows = vars(istraining),cols=vars(islearner,isgeneralizer,subid))+
  theme(legend.position = "top",legend.direction = "horizontal",legend.key.width = unit(dev.size()[1] / 10, "inches"))
```


### Location of errors
At which locations, do participants make more mistakes?

```{r}

#fcdf.similarity.perblock = generate_RDM(fc_df, splitby_var=c("subid","blocknumber_withinsess","istraining"), 
#             sortby_var=c("stim_x","stim_y"), 
#             similarity_var=c("choosen_locid","stim_locid"), 
#             specs_var=c("subid","isgeneralizer","islearner","blocknumber_withinsess","istraining"))

fcdf_sumloc = fc_df%>%
    aggregate_data(groupbyvars = c("subid","stim_id"),
                   yvars = c("resp_correct"),
                   stats =c("mu"),
                   additionalvars = c("isgeneralizer","islearner","istraining","stim_x","stim_y"))%>%
    change_cols_name(oldnames = "mu_resp_correct","accuracy")%>%
  mutate(islearner = factor(islearner,levels = c(0,1),labels = c("non-learner","learner")),
         isgeneralizer = factor(isgeneralizer,levels = c(0,1),labels = c("non-generalizer","generalizer")))
ggplot(fcdf_sumloc,aes(x=stim_x,y=stim_y,fill=accuracy))+
    geom_tile(linewidth=0.8,width=0.4,height=0.4)+
  scale_colour_viridis_c(aesthetics = c("fill"))+
  facet_nested(cols=vars(islearner,isgeneralizer,subid),rows=vars(istraining))+
  theme(legend.position = "top",legend.direction = "horizontal",legend.key.width = unit(dev.size()[1] / 10, "inches"))
```


### x confusion matrix when distractor is from same row  and y confusion matrix when distractor is from same column
```{r}
fcdf_sumlocx = fc_df%>%
  ## calculate for each participant, at each stimuli, how many trials where distractor and goal have same y and participant responded
  filter(stim_y == distractor_y)%>%
  group_by(subid,stim_id)%>%
  mutate(n_2afctrials_sameywithresp=n())%>%
  ungroup()%>%
  
  ## calculate for each participant, at each stim, what is the proportion of trials that chose an option with x=-1,-.5,... etc
    aggregate_data(groupbyvars = c("subid","stim_id","choosen_x"),
                   yvars = c("expt_index"),
                   stats =c("n"),
                   additionalvars = c("isgeneralizer","islearner","istraining","stim_x","n_2afctrials_sameywithresp"))%>%
    change_cols_name(oldnames = "n_expt_index","n_trials_choosex")%>%
  mutate(p_trials_choosex = n_trials_choosex/n_2afctrials_sameywithresp)%>%
  
  ## calcuate for each participant, at each stim_x, what is the average proportion of trials that chose an option with x=-1,-.5,... etc
  aggregate_data(groupbyvars = c("subid","istraining","stim_x","choosen_x"),
                   yvars = c("p_trials_choosex"),
                   stats =c("mu"),
                   additionalvars = c("isgeneralizer","islearner"))%>%
  change_cols_name(oldnames = c("mu_p_trials_choosex","stim_x","choosen_x"),
                   newnames = c("mu_p_trials","stim_loc","choosen_loc"))%>%
  mutate(confusionmatforaxis="x")

fcdf_sumlocy = fc_df%>%
  ## calculate for each participant, at each stimuli, how many trials where distractor and goal have same x and participant responded
  filter(stim_x == distractor_x)%>%
  group_by(subid,stim_id)%>%
  mutate(n_2afctrials_samexwithresp=n())%>%
  ungroup()%>%
  
  ## calculate for each participant, at each stim, what is the proportion of trials that chose an option with y=-1,-.5,... etc
    aggregate_data(groupbyvars = c("subid","stim_id","choosen_y"),
                   yvars = c("expt_index"),
                   stats =c("n"),
                   additionalvars = c("isgeneralizer","islearner","istraining","stim_y","n_2afctrials_samexwithresp"))%>%
    change_cols_name(oldnames = "n_expt_index","n_trials_choosey")%>%
  mutate(p_trials_choosey = n_trials_choosey/n_2afctrials_samexwithresp)%>%
  ## calcuate for each participant, at each stim_x, what is the average proportion of trials that chose an option with x=-1,-.5,... etc
  aggregate_data(groupbyvars = c("subid","istraining","stim_y","choosen_y"),
                   yvars = c("p_trials_choosey"),
                   stats =c("mu"),
                   additionalvars = c("isgeneralizer","islearner"))%>%
  change_cols_name(oldnames = c("mu_p_trials_choosey","stim_y","choosen_y"),
                   newnames = c("mu_p_trials","stim_loc","choosen_loc"))%>%
  mutate(confusionmatforaxis="y")
  
fcdf_sumloc = rbind(fcdf_sumlocx,fcdf_sumlocy)%>%
  mutate(islearner = factor(islearner,levels = c(0,1),labels = c("non-learner","learner")),
         isgeneralizer = factor(isgeneralizer,levels = c(0,1),labels = c("non-generalizer","generalizer")))

ggplot(fcdf_sumloc,aes(x=stim_loc,y=choosen_loc,fill=mu_p_trials))+
    geom_tile(linewidth=0.8,width=0.4,height=0.4)+
  scale_colour_viridis_c(aesthetics = c("fill"))+
  scale_y_continuous(trans="reverse")+
  facet_nested(rows = vars(confusionmatforaxis,istraining),cols=vars(islearner,isgeneralizer,subid))+
  theme(legend.position = "top",legend.direction = "horizontal")
```

### quadrant error: two-step away but cross column and row trials (exclude training and corner stimuli)
```{r}
fcdf_quaderr = fc_df%>%
  ## select two-step away trials for non-training stimuli and non-corner stimuli
  filter(istraining=="validation+test" & abs(stim_x*stim_y)<1 & distractor_distx==0.5 & distractor_disty==0.5)
# to check if selection if correct: ggplot(data=fcdf_quaderr,aes(x=stim_x,y=stim_y,fill=subid,color=subid))+geom_point()+facet_nested(cols=vars(subid))+theme(legend.position="top")

fcdf_quaderr = fcdf_quaderr%>%
  group_by(subid)%>%
  mutate(n_selectedtrials=n())%>%
  ungroup()%>%
  mutate(distractor_samexsign = sign(distractor_x) == sign(stim_x),
         distractor_sameysign = sign(distractor_y) == sign(stim_y))%>%
  mutate(distractor_samequadrant = distractor_samexsign&distractor_sameysign)%>%
  mutate(distractor_samexsign = factor(distractor_samexsign, levels=c(TRUE,FALSE), labels=c("same x sign","different x sign")),
         distractor_sameysign = factor(distractor_sameysign, levels=c(TRUE,FALSE), labels=c("same y sign","different y sign")),
         distractor_samequadrant = factor(distractor_samequadrant, levels=c(TRUE,FALSE), labels=c("same quadrant","different quadrant"))
         )

fcdf_quaderr_sub = fcdf_quaderr%>%
  aggregate_data(groupbyvars = c("subid","distractor_samequadrant"),
                 yvars = c("resp_correct","resp_rt"),
                 stats="mu",
                 additionalvars = c("islearner","isgeneralizer"))%>%
  change_cols_name(c("mu_resp_correct","mu_resp_rt"),c("accuracy","RT"))%>%
  mutate(islearner = factor(islearner,levels = c(0,1),labels = c("non-learner","learner")),
         isgeneralizer = factor(isgeneralizer,levels = c(0,1),labels = c("non-generalizer","generalizer")))

fcdf_quaderr_sum = fcdf_quaderr_sub%>%
  aggregate_data(groupbyvars = c("islearner","isgeneralizer","distractor_samequadrant"),
                 yvars = c("accuracy","RT"),
                 stats=c("mu","se"))

ggplot(data=fcdf_quaderr_sum,aes(x=distractor_samequadrant,fill=distractor_samequadrant,color=distractor_samequadrant))+
  geom_col(aes(y=mu_accuracy),position = position_dodge2(1),alpha=0.5)+
  geom_errorbar(aes(ymin=mu_accuracy-se_accuracy,
                    ymax=mu_accuracy+se_accuracy),
                position = position_dodge(1),width=0.4)+
  geom_point(data=fcdf_quaderr_sub,aes(y=accuracy),position = position_dodge(1))+
  geom_line(data=fcdf_quaderr_sub,aes(y=accuracy,group=subid))+
  facet_nested(cols = vars(isgeneralizer))

ggplot(data=fcdf_quaderr_sum,aes(x=distractor_samequadrant,fill=distractor_samequadrant,color=distractor_samequadrant))+
  geom_col(aes(y=mu_RT),position = position_dodge2(1),alpha=0.5)+
  geom_errorbar(aes(ymin=mu_RT-se_RT,
                    ymax=mu_RT+se_RT),
                position = position_dodge(1),width=0.4)+
  geom_point(data=fcdf_quaderr_sub,aes(y=RT),position = position_dodge(1))+
  geom_line(data=fcdf_quaderr_sub,aes(y=RT,group=subid))+
  facet_nested(cols = vars(isgeneralizer))

```







# debrief

```{r}
debrief_data = read.csv(file.path(data_dir,"debrief_data.csv",fsep="/"))
cluster_data = read.csv(file.path(data_dir,"cluster_data.csv",fsep="/"))
debrief_cluster_data = left_join(cluster_data,debrief_data,by=c("prolificid","subid"))%>%
  filter(!(subid %in% remove_sub))%>%
  mutate(islearner = subid %in% learnerids,
         isgeneralizer = subid %in% generalizerids,
         symbol_side = if_else(floor(symID/5)==0,"L","R"),
         symbol_axisloc = mod(symID,5)-2)%>%
  mutate(islearner = factor(islearner,levels = c(FALSE,TRUE),labels = c("non-learner","learner")),
         isgeneralizer = factor(isgeneralizer,levels = c(FALSE,TRUE),labels = c("non-generalizer","generalizer")))
```


```{r}
generalizer_mat = list()
nongeneralizer_mat = list()
for (pid in unique(debrief_cluster_data$subid)){
  curr_data = filter(debrief_cluster_data,subid==pid)%>%
    dplyr::select(-c(ends_with("sx"),ends_with("sy"),"init_x","init_y","X.x","X.y"))
  curr_data = arrange(curr_data,symID)
  sym_info = curr_data[,c("symID","symbol_side","symbol_axisloc")]
  sym_info_1 = change_cols_name(sym_info,oldnames = colnames(sym_info),newnames = paste0(colnames(sym_info),"_1"))
  sym_info_2 = change_cols_name(sym_info,oldnames = colnames(sym_info),newnames = paste0(colnames(sym_info),"_2"))

  sym_loc_mat = as.matrix(curr_data[,c("final_x","final_y")])
  dist_mat = pdist(sym_loc_mat)
  diag(dist_mat)=NaN
  
  if (pid %in% generalizerids){
    generalizer_mat = append(generalizer_mat,list(dist_mat))
  } else{
    nongeneralizer_mat = append(nongeneralizer_mat,list(dist_mat))
  }
  
  dist_df = data.frame(reshape::melt.array(dist_mat))
  colnames(dist_df) = c("symID_1","symID_2","distance")
  dist_df = dist_df%>%
    mutate(symID_1=symID_1-1,
           symID_2=symID_2-1,
           )
  dist_df = left_join(left_join(dist_df,sym_info_1,by="symID_1"),sym_info_2,by="symID_2")
  
  plot_name = paste(pid,"\n",unique(curr_data$islearner),unique(curr_data$isgeneralizer))
  (p2 = ggplot(data=dist_df,aes(x=symID_1,y=symID_2))+
      geom_tile(aes(fill=distance))+
      scale_x_continuous(breaks=unique(dist_df$symID_1),
                         labels=paste(sym_info$symbol_side,sym_info$symbol_axisloc,sep="_"))+
      scale_y_continuous(breaks=unique(dist_df$symID_2),
                         labels=paste(sym_info$symbol_side,sym_info$symbol_axisloc,sep="_"),
                         trans="reverse")+
      scale_fill_distiller(aesthetics = c("fill"),palette = "YlOrRd",na.value = "white")+
      labs(subtitle = "RDM from Arrangements",
           x="symbol",y="symbol",
           )+
      theme(legend.position = "top",
            aspect.ratio = 1,
            axis.line = element_blank(),
            legend.key.width = unit(dev.size()[1] / 10, "inches"))
    )
  (p1=ggplot(data=curr_data,aes(x=final_x,y=final_y))+
      geom_text(aes(label=paste(symbol_side,symbol_axisloc,sep="_"),
                    color=symbol_side,fontface="bold"))+
      labs(x="x",y="y",subtitle="Arrangement")+
      theme(legend.position = "top",legend.direction = "horizontal")
      )
  p3 = ggplot()+
    geom_textbox(aes(x=0,y=0),
                 width = unit(0.5, "npc"),
                 label=paste0("debrief: ", unique(curr_data$clusterRationale)),
                 size=4)+
    theme(axis.line = element_blank(),
          axis.text = element_blank(),
          axis.ticks = element_blank(),
          axis.title = element_blank())
      
  p=grid.arrange(p1,p2,p3,nrow=1,widths=c(1,1,0.5),
                 top=grid::textGrob(plot_name,
                              gp = grid::gpar(fontface = "bold", fontsize = 20)))
  ggsave(file.path(result_dir,'individualmaps',"participant_clustertask",paste0(pid,'.png')),plot = p,width = 16,height = 9)  
}
```

```{r}

mean_rdm_g = Reduce("+", generalizer_mat) / length(generalizer_mat)
mean_rdm_ng = Reduce("+", nongeneralizer_mat) / length(nongeneralizer_mat)

dist_df_g = data.frame(reshape::melt.array(mean_rdm_g))
colnames(dist_df_g) = c("symID_1","symID_2","distance")
dist_df_g = dist_df_g%>%
  mutate(symID_1=symID_1-1,
         symID_2=symID_2-1,
         group = "Generalizers"
         )
dist_df_ng = data.frame(reshape::melt.array(mean_rdm_ng))
colnames(dist_df_ng) = c("symID_1","symID_2","distance")
dist_df_ng = dist_df_ng%>%
  mutate(symID_1=symID_1-1,
         symID_2=symID_2-1,
         group = "nonGeneralizers"
         )
sym_info
dist_df = rbind(dist_df_g,dist_df_ng)
(p = ggplot(data=dist_df,aes(x=symID_1,y=symID_2))+
      facet_grid(cols=vars(group))+
      geom_tile(aes(fill=distance))+
      scale_x_continuous(breaks=unique(dist_df$symID_1),
                         labels=paste(sym_info$symbol_side,sym_info$symbol_axisloc,sep="_"))+
      scale_y_continuous(breaks=unique(dist_df$symID_2),
                         labels=paste(sym_info$symbol_side,sym_info$symbol_axisloc,sep="_"),
                         trans="reverse")+
      scale_fill_distiller(aesthetics = c("fill"),palette = "YlOrRd",na.value = "white")+
      labs(x="symbol",y="symbol")+
      theme(legend.position = "top",
            aspect.ratio = 1,
            axis.line = element_blank()
            )
    )
```

